% All information in this block is optional, comment out any lines you don't need
\title{Cover Letter}
\address{IIT Kharagpur, West Bengal, India}{}
\mobile{+91-9002966333}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{subbham@iitkgp.ac.in}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
\newcommand\tab[1][1cm]{\hspace*{#1}}
%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

%\section{Previous Research Experience}
Dear Recruiters, \\

\tab I, Subham Sekhar Sahoo, am a third year Undergraduate student in the \textbf{Indian Institute of Technology}, Kharagpur, India pursing a major in Electrical Engineering and a minor in Computer Science.\\

\tab I am interested in applying for the summer internship position. I was speaking to Ms. Atousa Torabi who was previously a Post Doctoral Associate at Disney Research and she suggested I apply for an internship at Disney based on my interests and work experience. I have had a great deal of experience in Machine Learning and Deep Learning. Hence I would like to work in the Machine Learning and Data-Analytics team. The 2 notable projects that interested me are - Kernel Predicting Convolutional Networks for Denoising Monte Carlo Renderings and Data-Driven Ghosting using deep Imitation Learning. I beleive my past internships, projects and strong academic background make me the ideal candidate for this position. \\

\tab In the summer 2017 I interned in the Autonomous Learning Group at \textbf{Max Planck Institute for Intelligent Systems}, Tuebingen (Germany) where I designed a deep learning model for extrapolation regression tasks for physical systems. I was also a former member in Autonomous Ground Vehicle Research Group, in my institute where my task completely revolved around deep learning. In addition I have also done relevant projects and possess the specific technical skills (as mentioned in my resume), which make me a good fit to the team. I'm also expecting a publication based on my work in MPI (pre-print to be made available soon).\\

\tab I believe that I would be an asset to your program. This internship would provide me with the ideal opportunity to assist your organization and to expand my research skills.

\end{document}
